Spherical harmonic analysis of faceted spheroids identifies shaping strategies and standardisation at Qianshangying (North China)

### 2025-09-19 analysis/paper/paper.qmd
updates

---
title: "Spherical harmonic analysis of faceted spheroids identifies shaping strategies and standardisation at Qianshangying (North China)"
author:
  - Ye Zhi:
      correspondence: "no"
      orcid: 
      institute:
        - ivpp1
        - ivpp2
        - UCAS
  - Shuwen Pei:
      correspondence: "yes"
      email: peishuwen@ivpp.ac.cn
      orcid: 
      institute:
        - ivpp1
        - ivpp2
  - Li Hao:
      correspondence: "no"
      orcid: 
      institute:
        - ALPHA
        - TPESRE
  - Dongdong Ma:
      correspondence: "no"
      orcid: 
      institute:
        - ivpp1
        - ivpp2
  - Ben Marwick:
      correspondence: "yes"
      email: bmarwick@uw.edu
      orcid: 0000-0001-7879-4531
      institute:
        - uw
institute:
  - ivpp1: Key Laboratory of Vertebrate Evolution and Human Origins, Institute of Vertebrate Paleontology and Paleoanthropology, Chinese Academy of Sciences, Beijing 100044, China
  - ivpp2: Key Scientific Research Base on Paleolithic Human Evolution and Paleogenetics (IVPP), SACH. Beijing, 100044, China
  - UCAS: University of Chinese Academy of Sciences, Beijing 100049, China
  - ALPHA: Group of Alpine Paleoecology and Human Adaptation (ALPHA), Institute of Tibetan Plateau Research, Chinese Academy of Sciences, Beijing 100101; 
  - TPESRE: State Key Laboratory of Tibetan Plateau Earth System, Resources and Environment (TPESRE), Beijing 100101
  - uw: Department of Anthropology, University of Washington, Seattle, WA, USA

>>>>

---
title: "Spherical harmonic analysis of faceted spheroids identifies shaping strategies and standardisation at Qianshangying (North China)"
author:
  - Ye Zhi:
      correspondence: "no"
      orcid: 
      institute:
        - ivpp1
        - ivpp2
        - UCAS
  - Shuwen Pei:
      correspondence: "yes"
      email: peishuwen@ivpp.ac.cn
      orcid: 
      institute:
        - ivpp1
        - ivpp2
  - Dongdong Ma:
      correspondence: "no"
      orcid: 
      institute:
        - ivpp1
        - ivpp2
  - Li Hao:
      correspondence: "no"
      orcid: 
      institute:
        - ALPHA
        - TPESRE
  - Ben Marwick:
      correspondence: "yes"
      email: bmarwick@uw.edu
      orcid: 0000-0001-7879-4531
      institute:
        - uw
institute:
  - ivpp1: Key Laboratory of Vertebrate Evolution and Human Origins, Institute of Vertebrate Paleontology and Paleoanthropology, Chinese Academy of Sciences, Beijing 100044, China
  - ivpp2: Key Scientific Research Base on Paleolithic Human Evolution and Paleogenetics (IVPP), SACH. Beijing, 100044, China
  - UCAS: University of Chinese Academy of Sciences, Beijing 100049, China
  - ALPHA: Group of Alpine Paleoecology and Human Adaptation (ALPHA), Institute of Tibetan Plateau Research, Chinese Academy of Sciences, Beijing 100101; 
  - TPESRE: State Key Laboratory of Tibetan Plateau Earth System, Resources and Environment (TPESRE), Beijing 100101
  - uw: Department of Anthropology, University of Washington, Seattle, WA, USA
